---
title: "Homework 4"
author: "Put Your Names Here"
date: "Due Friday, February 3 by 11:59 p.m."
output: github_document
---


## Instructions

Complete this assignment in this .Rmd, knit it and upload it to your github repository for homework 4 (which will be created once I know what the groups are). When you upload your files, make sure that you include **all** of the files that are generated (hw4.md, and the hw4_files folder, assuming that you did not rename the hw4.Rmd file). 

## Data

All domestic flights leaving George Bush Intercontinental Airport (IAH) in
Houston in 2011. There are 5 data sets to consider:

* `flights` [227,496 x 14]: Flight data.
* `weather` [8,723 x 14]: Hourly weather data.
* `planes` [2,853 x 9]: Plane metadata.
* `airports` [3,376 x 7]: Airport metadata.
* `states` [48 x 3]: (Lower 48) state data.

I have embeded a code chunk that loads the data, but won't print to your knitted .md file since I set `echo=FALSE` in the chunk options.

```{r, echo=FALSE, message=FALSE, cache=TRUE}
library(tidyverse)

# Load data sets. Note this assumes this .Rmd file is in the same directory as
# the data folder. Also, read_csv is an improved version of read.csv.
flights <- read_csv("data/flights.csv") %>% 
  mutate(date=as.Date(date))
weather <- read_csv("data/weather.csv") %>% 
  mutate(date=as.Date(date))
planes <- read_csv("data/planes.csv")
airports <- read_csv("data/airports.csv")
states <- read_csv("data/states.csv")
```

* * * 

## Question 1:

Plot a "time series" of the proportion of flights that were delayed by > 30 minutes on each day.  i.e.
 
* the x-axis should be some notion of time
* the y-axis should be the proportion.

Using this plot, indicate describe the
[seasonality](https://en.wikipedia.org/wiki/Seasonality) of when delays over 30
minutes tend to occur.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=6}

```


* * * 


## Question 2:

Some people prefer flying on older planes.  Even though they aren't as nice,
they tend to have more room.  Which airlines should these people favor?

```{r, echo=FALSE, fig.width=12, fig.height=6}

```


* * * 


## Question 3:

* What states did Southwest Airlines' **flight paths** tend to fly to?
* What states did Southwest Airlines' **flights** tend to fly to?

For example, Southwest Airlines Flight 60 to Dallas consists of a single flight
path, but since it flew 299 times in 2013, it would be counted as 299 flights.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=6}

```


* * * 


## Question 4:

I want to know proportionately what regions (NE, south, west, midwest) each 
carrier flies to/from Houston in the month of July.  Consider the `month()`
function from the `lubridate` package.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=6}

```
